Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
general updates3

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for advancing the field of quantum computing was the desire to simulate quantum
 systems in nature through the use of quantum systems, and by so doing to circumvent the exponential computing power needed to do these simulations
 on classical hardware. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum hardware
 and software that will allow for efficient quantum simulations of quantum chemical systems. Dr Abolfazl Bayat, a researcher at the Controlled
 Quantum Dynamics research group at UCL, states that "noise-resilient quantum computers would have transformative effects upon many fields,
 but especially in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of
 tantamount importance in quantum chemistry is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy
 eigenvalues define a great deal of properties of interest in the molecule. This is of great importance in for example the development of
 pharmaceuticals where companies have an extremely laborious testing and trials process, if a significant part of the initial testing process
 could be done in silico - this would represent significant savings and would better ensure that the pharmaceutical under development behaved as
 required prior to starting trials.

>>>>

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for advancing the field of quantum computing was the desire to simulate quantum
 systems in nature through the use of quantum systems, and by so doing to circumvent the exponential computing power needed to do these simulations
 on classical hardware. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum hardware
 and software that will allow for efficient quantum simulations of quantum chemical systems. Dr Abolfazl Bayat, a researcher at the Controlled
 Quantum Dynamics research group at UCL, states that ``noise-resilient quantum computers would have transformative effects upon many fields,
 but especially in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of
 tantamount importance in quantum chemistry is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy
 eigenvalues define a great deal of properties of interest in the molecule. This is of great importance in for example the development of
 pharmaceuticals where companies have an extremely laborious testing and trials process, if a significant part of the initial testing process
 could be done in silico - this would represent significant savings and would better ensure that the pharmaceutical under development behaved as
 required prior to starting trials.
